Appendix B: Code for analysis comparing to historical data

### 2018-12-03 appendix/appendixA.Rmd
rebuild from scratch

```{r knitr, include=FALSE}
knitr::opts_chunk$set(comment="", message=FALSE, warning = FALSE, cache=TRUE, dev="cairo_pdf", echo=TRUE)
```

@@

```{r}
tic()
options(mc.cores=parallel::detectCores())
log_dir <- "../data/observe_harvest_recruit" # Store the computed solution files here

@@

write_csv(det_sims, "../data/observe_harvest_recruit/det_sims.csv")
```

@@

```{r eval=!file.exists(file.path(log_dir, "meta.csv"))}
dir.create(log_dir)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = r, 
                             K = K, 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             scenario = meta[i, "scenario"][[1]])

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 0.00000002,
             timeout = 15000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

@@

We can read the stored solution from the log:

```{r}
meta <- meta_from_log(data.frame(model="gs", discount=discount), log_dir) %>% 
  mutate(scenario = as.character(scenario)) %>%
  left_join(meta) %>% 
  arrange(scenario)
alphas <- alphas_from_log(meta, log_dir)
```

@@

```{r pomdp_sims, eval=!file.exists(file.path(log_dir, "pomdp_sims.csv"))}
set.seed(12345)

@@

```{r overest, eval=!file.exists(file.path(log_dir, "pomdp_overest_sims.csv"))}
set.seed(12345)
true <- 3 # sigma_g = 0.15, sigma_m = 0
source(system.file("examples/pomdp_overestimates.R", package="sarsop")) # portable example code
pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation = models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "POMDP") # include a column labeling method
           },
           .id = "scenario"
  )
write_csv(pomdp_overest_sims, file.path(log_dir, "pomdp_overest_sims.csv"))
```

@@

@@

Hardware:

```{r}
system2("grep", c("MemTotal", "/proc/meminfo"), stdout = TRUE)
system2('grep', '-m 1 "model name" /proc/cpuinfo', stdout = TRUE)
```

Software:

```{r}
sessionInfo()
```

>>>>

```{r knitr, include=FALSE}
knitr::opts_chunk$set(comment="", message=FALSE, warning = FALSE, cache=FALSE, dev="cairo_pdf", echo=TRUE)
```

@@

```{r}
tic()
options(mc.cores=parallel::detectCores())
log_dir <- "../data/appendixA" # Store the computed solution files here

@@

write_csv(det_sims, "../data/appendixA/det_sims.csv")
```

@@

```{r}
dir.create(log_dir, FALSE)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = r, 
                             K = K, 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             scenario = meta[i, "scenario"][[1]])

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 1e-8,
             timeout = 15000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

@@

@@

```{r pomdp_sims}
set.seed(12345)

@@

```{r overest}
set.seed(12345)
true <- 3 # sigma_g = 0.15, sigma_m = 0
source(system.file("examples/pomdp_overestimates.R", package="sarsop")) # portable example code
pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation = models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "POMDP") # include a column labeling method
           },
           .id = "scenario"
  )
write_csv(pomdp_overest_sims, file.path(log_dir, "pomdp_overest_sims.csv"))
```

@@

# System Information

@@

### Hardware:

```{r}
system2("grep", c("MemTotal", "/proc/meminfo"), stdout = TRUE)
system2('grep', '"model name" /proc/cpuinfo', stdout = TRUE)
```

### Software:

```{r}
devtools::session_info()
```

### 2018-12-03 appendix/appendixB.Rmd
rebuild from scratch

@@

```{r knitr, include=FALSE}
knitr::opts_chunk$set(comment="", message=FALSE, warning = FALSE, cache=TRUE, dev="cairo_pdf")
```

@@

```{r plotting, include = FALSE}
## This chunk is optional, just tweaks plot appearance / fonts
library(printr)
library(ggthemes)
library(Cairo)
library(extrafont)
library(hrbrthemes)

@@

palette <- c("#D9661F", "#3B7EA1", "#6C3302",
             "#FDB515", "#00B0DA",  "#CFDD45")
colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: medium prior",
                      "biomass",
                      "catch"))
scale_colour_discrete <- function(...) scale_colour_manual(..., values=colors)
scale_fill_discrete <- function(...) scale_fill_manual(..., values=colors)
```

@@

```{r include = FALSE, eval = FALSE}
## Do the estimates make sense?  Consider simulation from models, 
## under this historical harvests, compared to historical trajectories
examples %>% ungroup() %>%
  select(year, scaled_biomass, scaled_catch, commonname) %>%
  gather(stock, biomass, -year, -commonname) %>%
  ggplot(aes(year, biomass, col=stock)) + 
  geom_line() + facet_wrap(~commonname, scales = "free")
```

@@

```{r}
options(mc.cores = parallel::detectCores()) # Reserve ~ 10 GB per core
log_dir <- "../data/ram_ex"
```

@@

```{r eval=FALSE}
dir.create(log_dir)
options(mc.cores = 1)

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 2e-6,
             timeout = 25000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

@@

```{r message=FALSE}
meta <- meta_from_log(data.frame(model="gs"), log_dir)  %>% 
  mutate(scenario = as.character(scenario)) %>%
  left_join(
    select(meta, sigma_m, commonname, scenario),   
    by = c("scenario", "sigma_m", "commonname")) %>% 
  arrange(scenario)
alphas <- alphas_from_log(meta, log_dir)
#models <- models_from_log(meta)
```

@@

write_csv(sims,file.path(log_dir, "ram_ex.csv"))
```

@@

```{r}
ram_ex <- read_csv(file.path(log_dir, "ram_ex.csv"))
ram_ex %>%
  filter(model %in% c("biomass", "catch", "POMDP", "CE", "TAC", "MSY")) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = colors) +
  facet_wrap(~commonname, scales = "free", ncol=1)  
```

@@

Hardware:

@@

Software:

```{r}
sessionInfo()
```

>>>>

\renewcommand{\thefigure}{S\arabic{figure}}

@@

```{r knitr, include=FALSE}
knitr::opts_chunk$set(comment = "", message = FALSE, 
                      warning = FALSE, cache = FALSE, 
                      dev = "cairo_pdf")
```

@@

```{r plotting, include = FALSE, cache = FALSE}
## This chunk is optional, just tweaks plot appearance / fonts
library(printr)
library(ggthemes)
library(Cairo)
library(extrafont)
library(hrbrthemes)

@@

palette <- c("#D9661F", "#3B7EA1", "#6C3302",
             "#FDB515", "#00B0DA",  "#CFDD45")
colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: medium prior",
                      "biomass",
                      "catch"))
## Overwriting is convenient, but breaks any plot not using these names!
scale_colour_discrete <- function(...) scale_colour_manual(..., values=colors)
scale_fill_discrete <- function(...) scale_fill_manual(..., values=colors)
```

@@

@@

```{r}
options(mc.cores = parallel::detectCores()) # Reserve ~ 10 GB per core
log_dir <- "../data/appendixB"
```

@@

```{r message = FALSE, output = "hide"}
dir.create(log_dir, FALSE)
options(mc.cores = 1)

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 2e-8,
             timeout = 26000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

@@

@@

write_csv(sims,file.path(log_dir, "appendixB.csv"))
```

@@

```{r}
appendixB <- read_csv(file.path(log_dir, "appendixB.csv"))
appendixB %>%
  filter(model %in% c("biomass", "catch", "POMDP", "CE", "TAC", "MSY")) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = colors) +
  facet_wrap(~commonname, scales = "free", ncol=1)  
```

@@

### Hardware:

@@

### Software:

```{r}
devtools::session_info()
```
